---
title       : WebPageAnalyser
subtitle    : Coursera. Developing Data Products.
author      : AM
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---
<!-- Limit image width and height -->
<style type='text/css'>
img {
    max-height: 400px;
    max-width: 400px;
}
</style>

## Introduction

WebPageAnalyser is an example of shiny application. It demonstrates web page scraping, parsing HTML and presentation results on graphic. This presentation describes R code used in the application.

WebPageAnalyser based on packages: 

```{r}
library(XML) # Used to parse HTML code
library(ggplot2) # Used to plot grafics 
library(scales)  # Used to scale grafics
```
---

## Load and parse HTML page
Code chunk presented below implements web page scraping and parsing HTML content.
The result is a list of words used in the text on analyzed web page.
```{r}
# Fetch html page and merge all strings to one. 
web.content <- paste(readLines("http://news.yahoo.com"),"\n", collapse='')
# Parse html.
web.tree <- htmlTreeParse(web.content, asText=TRUE, useInternalNodes=T)
# Extract text content.     
web.text <- paste(xpathSApply(web.tree, '//p', xmlValue),' ', collapse=' ')
# Parse text to create word list.     
web.words <- tolower(unlist(strsplit(web.text,"[ .,;!?\"\\[\\)\\(]")))
```
---

## Processing word list
Word list obtained above used to builed table with words frequencies. 
```{r}
# Build table with words frequencies.   
web.words.table <- data.frame(table(web.words[nchar(web.words)>2]), stringsAsFactors=F)
# Sort table by frequencies  
web.words.table <- web.words.table[order(web.words.table$Freq, decreasing=T),]
# Add word rank to the table
web.words.table[, 3] <- seq(nrow(web.words.table))
# Change row and column names
names(web.words.table) <- c("Word","Freq","Rank"); rownames(web.words.table) <- NULL
```
The result of this code is a table:
```{r, echo=FALSE, }
head(web.words.table, 2)
```
---

## Result
WebPageAnalyser used ggplot function to build grafic.
```{r}
ggplot(web.words.table, aes(x=Rank, y=Freq)) +
      geom_point(size=3) +
      xlab("Rank") + ylab("Freq.") + 
      theme_bw() + 
      scale_x_log10(breaks = trans_breaks('log10', function(x) 10^x),
                    labels = trans_format('log10', math_format(10^.x)))
```
